Title

### 2013-02-07 inc/model_results/shapes/shapes.tex
rephrase about spherical pulse increase

The initial `space-time' eccentricity \ref{eq:define_xi}, $\xi ( 0 ) = v_{{ \scriptscriptstyle 0}} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and `cigar-like' ($ \sigma_{ z } ( 0 ) > \sigma_{ \smallT } ( 0 ) $) pulses.
%TODO rewrite using w?
Unlike most simulations in this paper, the pulses in this simulation are not calculated from laser and photocathode parameters, but are rather defined directly.
The initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ while in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Since the initial pulse volumn is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} ($ N = 10^{6} $ electrons in the bunch) than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} ($ N = 10^{0} $).
The pulse velocity is $ v_{{ \scriptscriptstyle 0}} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a prolate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for oblate (a ``cigar'') having $\xi=3$.
  }
  \label{fig:compare_shape}
%\caption
%{
%Comparison of the propagation dynamics of disk-like ($ \xi (0) = 0.1 $), spherical ($ \xi (0) = 1 $) and cigar-like ($ \xi (0) = 10 $) pulses, generated from a 261nm laser driven Ta photocathode in a 20kV DC electron gun, at \subref{fig:compare_shape_N1} negligible charge densities ($ N = 10^{0} $) and \subref{fig:compare_shape_N1e6} charge densities suitable for single shot UED studies ($ N = 10^{6} $): the normalized transverse beam width ($ \sqrt{ \sigma_{\smallT} / \sigma_{\smallT} ( 0 ) } $) (solid line) and normalized longitudinal pulse width ($ \sqrt{ \sigma_{z} / \sigma_{z} ( 0 ) } $) (dashed line).
%}
\end{figure}

The bunch propagation dynamics for negligible pulse charge density ($ N = 10^{0} $) shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} display the trends expected from the initial photoemission conditions.
%In particular, in the initially spherical case ($ \sigma_{\smallT} (0) = \sigma_{z} (0) $), the transverse bunch width $ \sqrt{2 \sigma_{\smallT}} $ expands twice as rapidly as the longitudinal length $ \sqrt{2 \sigma_{z}} $ due to the factor of two difference in the initial momentum variances $ \Delta p_{\alpha} $ and the zero initial pulse chirp ($ \gamma_{\alpha} = 0 $).
In particular, in the initially spherical case ($ \sigma_{\smallT} (0) = \sigma_{z} (0) $), the transverse bunch width $ \sqrt{2 \sigma_{\smallT}} $ expands more rapidly than the longitudinal length $ \sqrt{2 \sigma_{z}} $ due to the factor of two difference in the initial momentum variances $ \Delta p_{\alpha} $ ( with zero initial pulse chirp, i.e. $ \gamma_{\alpha} = 0 $).
Naturally, for initially non-spherical electron bunches, the pulse propagation model also shows that the relative bunch broadening $ \sqrt{ \sigma_{\alpha} / \sigma_{\alpha} (0) } $ for comparable $ \eta_{\alpha} $ is greatest for the smallest initial $ \sigma_{\alpha} (0) $; that is both disk- and cigar-like pulses are initially driven towards the spherical regime.
In all cases, this intrinsic electron pulse broadening due to non-zero $ \eta_{\alpha} $ generates a momentum chirp across the electron bunch; in the longitudinal dimension the faster electrons photoemitted with larger excess energy leading the slower electrons.

>>>>

The initial `space-time' eccentricity \ref{eq:define_xi}, $\xi ( 0 ) = v_{{ \scriptscriptstyle 0}} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and `cigar-like' ($ \sigma_{ z } ( 0 ) > \sigma_{ \smallT } ( 0 ) $) pulses.
%TODO rewrite using w?
For simplicity, and unlike most simulations in this paper, the pulses in this simulation are not calculated from laser and photocathode parameters, but are rather defined directly.
The initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ while in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Since the initial pulse volumn is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} ($ N = 10^{6} $ electrons in the bunch) than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} ($ N = 10^{0} $).
The pulse velocity is $ v_{{ \scriptscriptstyle 0}} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a prolate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for oblate (a ``cigar'') having $\xi=3$.
  }
  \label{fig:compare_shape}
\end{figure}

The bunch propagation dynamics for negligible pulse charge density ($ N = 10^{0} $) shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} display the trends expected from the initial photoemission conditions.
In particular, in the initially spherical case ($ \sigma_{\smallT} (0) = \sigma_{z} (0) $), the transverse bunch width $ \sqrt{2 \sigma_{\smallT}} $ expands roughly twice as rapidly as the longitudinal length $ \sqrt{2 \sigma_{z}} $ due to the factor of two difference in the initial momentum variances $ \Delta p_{\alpha} $ and the artificially zero initial pulse chirp ($ \gamma_{\alpha} = 0 $).
Naturally, for initially non-spherical electron bunches, the pulse propagation model also shows that the relative bunch broadening $ \sqrt{ \sigma_{\alpha} / \sigma_{\alpha} (0) } $ for comparable $ \eta_{\alpha} $ is greatest for the smallest initial $ \sigma_{\alpha} (0) $; that is both disk- and cigar-like pulses are initially driven towards the spherical regime.
In all cases, this intrinsic electron pulse broadening due to non-zero $ \eta_{\alpha} $ generates a momentum chirp across the electron bunch; in the longitudinal dimension the faster electrons photoemitted with larger excess energy leading the slower electrons.
